A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
First draft of equivalence of McSplit and CP-FC bounds

@@

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative numbers of instances solved over time for the maximum
    common connected subgraph problem on the large subgraph isomorphism benchmark
    suite.} \label{figure:sip-cumulative}
\end{figure}

@@

CP-FC uses a soft all-different constraint to compute a bound, which requires
running a matching algorithm on a supporting compatibility graph.  Careful
thought shows that \McSplit\ computes the same bound, but using a simple
counting loop (\cref{McSplitAlg}, \lineref{CalcBound})---this is only possible
because of the disjoint nature of the domains.

>>>>

\newcommand{\graphB}{\mathcal{B}}

@@

\begin{figure}[htb]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative numbers of instances solved over time for the maximum
    common connected subgraph problem on the large subgraph isomorphism benchmark
    suite.} \label{figure:sip-cumulative}
\end{figure}

@@

CP-FC uses a soft all-different constraint to compute a bound, which requires
running a matching algorithm on a supporting compatibility graph.  We now
show that \McSplit\ computes the same bound, but using a simple
counting loop (\cref{McSplitAlg}, \lineref{CalcBound})---this is possible
because of the disjoint nature of the domains.

To illustrate the method used by CP-FC to calculate a bound, we consider the
input graphs $\graphG$ and $\graphH$ in \cref{fig:alg1}. Suppose that the
variable corresponding to vertex 1 has been matched to the value corresponding
to vertex $a$, and that no other assignments have been made.  In the
terminology of \McSplit, we now have two label classes: $\langle \{2,3\},
\{d,f\} \rangle$ and $\langle \{4,5\}, \{b,c,e\} \rangle$.  CP-FC represents
this state by storing the domain of each remaining variable: 2 and 3 each
have the domain $\{d,f\}$; 4 and 5 each have the domain $\{b,c,e\}$.

As described previously, the \McSplit\ algorithm finds the size of the smaller
set in each label class, and adds these sizes to the size of the current
mapping, giving a bound of 5.  CP-FC uses the compatibility graph $\graphB$ in
\cref{fig:cpfc-bipartite} to calculate an upper bound; variables are
represented by vertices on the left, values are represented by vertices on the
right, and a variable may take a value if and only if the corresponding
vertices are adjacent.  The upper bound is calculated by CP-FC by computing a
maximum matching on this bipartite graph, and adding the size of this matching
to the size of the current mapping.

The vertices in the bipartite graph are coloured to emphasise how they
correspond to the two label classes.  Each label class corresponse to a
complete bipartite graph, and there are no edges between the components
corresponding to different label classes.  Clearly, a maximum matching in
$\graphB$ must be the union of the maximum matching in each complete bipartite
subgraph, and each of these matchings in turn have the same size as the smaller
of the left and right sets of vertices.  It follows that the CP-FC bound is
identical to the \McSplit\ bound.

\begin{figure}[htb]
\centering
% Bipartite graph TikZ based on code from
% https://tex.stackexchange.com/a/15094/61367
\definecolor{myblue}{RGB}{240,240,240}
\definecolor{mygreen}{RGB}{120,120,120}
\usetikzlibrary{positioning,chains,fit,shapes,calc}

\begin{tikzpicture}[thick,
  every node/.style={draw,circle},
  class1node/.style={fill=myblue},
  class2node/.style={fill=mygreen},
  every fit/.style={ellipse,draw,inner sep=-2pt,text width=2cm}
]

\begin{scope}[start chain=going below,node distance=3mm]
\foreach \i in {2,3}
  \node[class1node,on chain] (f\i) [label=left: \i] {};
\end{scope}

\begin{scope}[yshift=-1.8cm,start chain=going below,node distance=3mm]
\foreach \i in {4,5}
  \node[class2node,on chain] (f\i) [label=left: \i] {};
\end{scope}

\begin{scope}[xshift=2.2cm,start chain=going below,node distance=3mm]
\foreach \i in {d,f}
  \node[class1node,on chain] (s\i) [label=right: \i] {};
\end{scope}

\begin{scope}[xshift=2.2cm,yshift=-1.5cm,start chain=going below,node distance=3mm]
\foreach \i in {b,c,e}
  \node[class2node,on chain] (s\i) [label=right: \i] {};
\end{scope}

% the edges
\draw (f2) -- (sd);
\draw (f3) -- (sd);
\draw (f2) -- (sf);
\draw (f3) -- (sf);

\draw (f4) -- (sb);
\draw (f4) -- (sc);
\draw (f4) -- (se);
\draw (f5) -- (sb);
\draw (f5) -- (sc);
\draw (f5) -- (se);
\end{tikzpicture}

\caption{A bipartite graph of the type used to calculate a bound in CP-FC}
\label{fig:cpfc-bipartite}
\end{figure}
